Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-07 paper/experiments.tex
New schematic of classE PA
Data for benchmark functions

\begin{table*}[tp]
    \centering
    \caption{Optimization results of the benchmark functions}
    \label{tab:result_analytical}
    \begin{tabular}{lllllllllll}
        \toprule
        Function           & MACE-1 & LCB-1  & EI-1  & MACE-4  & BLCB-4  & EI-LP-4 & qKG-4 & qEI-4  \\ \midrule
         Branin            &        &        &       &         &         &         &       &        \\
         Alpine1           &        &        &       &         &         &         &       &        \\
         Hartmann6         &        &        &       &         &         &         &       &        \\
         Eggholder         &        &        &       &         &         &         &       &        \\
         Ackley2           &        &        &       &         &         &         &       &        \\
         Rosenbrock2       &        &        &       &         &         &         &       &        \\
         Ackley10          &        &        &       &         &         &         &       &        \\
         Rosenbrock10      &        &        &       &         &         &         &       &        \\
        \bottomrule
    \end{tabular}
\end{table*}

@@

\begin{table}[]
    \centering
    \caption{Optimization results of the operational amplifier}
    \label{tab:result_opamp}
    \begin{tabular}{llll}
        \toprule
        Algorithm & Results     \\ \midrule
        MACE-1    & 0.0$\pm$0.0 \\
        LCB-1     & 0.0$\pm$0.0 \\
        EI-1      & 0.0$\pm$0.0 \\
        MACE-4    & 0.0$\pm$0.0 \\
        BLCB-1    & 0.0$\pm$0.0 \\
        EI-LP-4   & 0.0$\pm$0.0 \\
        \bottomrule
    \end{tabular}
\end{table}

@@

\subsection{ClassE Power Amplifier}

\begin{figure}[htbp]
    \begin{center}
        \centerline{\includegraphics[width=\columnwidth]{./img/classE.png}}
        \caption{Schematic of the power amplifier\textcolor{red}{TODO: replace this schematic with eps file} }
        \label{fig:schPA}
    \end{center}
\end{figure}

>>>>

% \begin{table*}[tp]
%     \tiny
%     \centering
%     \caption{Optimization results of the benchmark functions}
%     \label{tab:result_analytical}
%     \begin{tabular}{lllllllllll}
%         \toprule
%         Function    & MACE-1             & LCB-1                 &  EI-1                 &  MACE-4               & BLCB-4                &  EI-LP-4              & qKG-4                   & qEI-4                     \\ \midrule
%         Eggholder   & 88$\pm$76          &  1.5e+2$\pm$1.1e2     &  1.7e2$\pm$1.3e2      &  46$\pm$41            &  57$\pm$36            &  45$\pm$56            &  1.1e2$\pm$68  &  72$\pm$52            & \\
%         Branin      & 1e-5$\pm$1.3e-5    &  6.9e-5$\pm$1.1e-4    &  0.016$\pm$0.016      &  4.6e-6$\pm$6.6e-6    &  4.3e-5$\pm$6.3e-5    &  0.021$\pm$0.018      &  0.27$\pm$0.27 &  3.3e-4$\pm$1.1e-3    & \\
%         Alpine1     & 2.7$\pm$1.1        &  5.7$\pm$1.8          &  2.5$\pm$1.6          &  0.9$\pm$0.84         &  1.9$\pm$0.94         &  1$\pm$0.46           &  3$\pm$1.1     &  2.7$\pm$1.1          & \\
%         Hart6       & 0.065$\pm$0.062    &  0.13$\pm$0.12        &  0.11$\pm$0.15        &  0.028$\pm$0.052      &  0.064$\pm$0.062      &  0.054$\pm$0.056      &  0.47$\pm$0.19 &  0.19$\pm$0.12        & \\
%         Ackley      & 1.7$\pm$1.1        &  1.6$\pm$0.93         &  1$\pm$0.99           &  1.1$\pm$0.89         &  1.4$\pm$1            &  0.28$\pm$0.25        &  5.6$\pm$1.8   &  2.9$\pm$1            & \\
%         Rosenbrock  & 0.026$\pm$0.051    &  0.02$\pm$0.021       &  14$\pm$9.5           &  9.5e-4$\pm$9.4e-4    &  1.9e-3$\pm$1.8e-3    &  2.7$\pm$2.1          &  5$\pm$3.7     &  10$\pm$15            & \\
%         G05         & 3.1$\pm$0.45       &  3.1$\pm$0.52         &  19$\pm$0.65          &  2.6$\pm$0.54         &  3.3$\pm$0.74         &  18$\pm$0.61          &  18$\pm$0.76   &  18$\pm$0.5           & \\
%         G07         & 500$\pm$300        &  520$\pm$290          &  1400$\pm$640         &  160$\pm$50           &  410$\pm$130          &  720$\pm$330          &  710$\pm$410   &  660$\pm$340          & \\
%         \bottomrule
%     \end{tabular}
% \end{table*}

\begin{table*}[t]
    \centering
    \caption{Optimization results of the benchmark functions}
    \label{tab:result_analytical}
    \begin{tabular}{lllllllllll}
        \toprule
                    & MACE-1                & LCB-1                 &  EI-1                 &                & \\ \midrule
        Eggholder   & 88$\pm$76             &  1.5e+2$\pm$1.1e2     &  1.7e2$\pm$1.3e2      &                & \\
        Branin      & 1e-5$\pm$1.3e-5       &  6.9e-5$\pm$1.1e-4    &  0.016$\pm$0.016      &                & \\
        Alpine1     & 2.7$\pm$1.1           &  5.7$\pm$1.8          &  2.5$\pm$1.6          &                & \\
        Hart6       & 0.065$\pm$0.062       &  0.13$\pm$0.12        &  0.11$\pm$0.15        &                & \\
        Ackley      & 1.7$\pm$1.1           &  1.6$\pm$0.93         &  1$\pm$0.99           &                & \\
        Rosenbrock  & 0.026$\pm$0.051       &  0.02$\pm$0.021       &  14$\pm$9.5           &                & \\
        G05         & 3.1$\pm$0.45          &  3.1$\pm$0.52         &  19$\pm$0.65          &                & \\
        G07         & 500$\pm$300           &  520$\pm$290          &  1400$\pm$640         &                & \\
        \hline
                    &  MACE-4               & BLCB-4                &  EI-LP-4              & qKG-4          & qEI-4                 \\ \midrule
        Eggholder   &  46$\pm$41            &  57$\pm$36            &  45$\pm$56            &  1.1e2$\pm$68  &  72$\pm$52            \\
        Branin      &  4.6e-6$\pm$6.6e-6    &  4.3e-5$\pm$6.3e-5    &  0.021$\pm$0.018      &  0.27$\pm$0.27 &  3.3e-4$\pm$1.1e-3    \\
        Alpine1     &  0.9$\pm$0.84         &  1.9$\pm$0.94         &  1$\pm$0.46           &  3$\pm$1.1     &  2.7$\pm$1.1          \\
        Hart6       &  0.028$\pm$0.052      &  0.064$\pm$0.062      &  0.054$\pm$0.056      &  0.47$\pm$0.19 &  0.19$\pm$0.12        \\
        Ackley      &  1.1$\pm$0.89         &  1.4$\pm$1            &  0.28$\pm$0.25        &  5.6$\pm$1.8   &  2.9$\pm$1            \\
        Rosenbrock  &  9.5e-4$\pm$9.4e-4    &  1.9e-3$\pm$1.8e-3    &  2.7$\pm$2.1          &  5$\pm$3.7     &  10$\pm$15            \\
        G05         &  2.6$\pm$0.54         &  3.3$\pm$0.74         &  18$\pm$0.61          &  18$\pm$0.76   &  18$\pm$0.5           \\
        G07         &  160$\pm$50           &  410$\pm$130          &  720$\pm$330          &  710$\pm$410   &  660$\pm$340          \\
        \bottomrule
    \end{tabular}
\end{table*}

@@

\begin{table}[h]
    \centering
    \caption{Optimization results of the operational amplifier}
    \label{tab:result_opamp}
    \begin{tabular}{llll}
        \toprule
        Algorithm & Results     \\ \midrule
        MACE-1    & 0.0$\pm$0.0 \\
        LCB-1     & 0.0$\pm$0.0 \\
        EI-1      & 0.0$\pm$0.0 \\
        MACE-4    & 0.0$\pm$0.0 \\
        BLCB-1    & 0.0$\pm$0.0 \\
        EI-LP-4   & 0.0$\pm$0.0 \\
        \bottomrule
    \end{tabular}
\end{table}

@@

\subsection{Class-E Power Amplifier}

\begin{figure}[htbp]
    \begin{center}
        \centerline{\includegraphics[width=\columnwidth]{./img/classE.eps}}
        \caption{Schematic of the power amplifier}
        \label{fig:schPA}
    \end{center}
\end{figure}
